---
title: "Lab 5"
author: "naftali"
date: "2024-12-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load data
A summary of the basic statistics concerning the players' entire career.
Hint: Names of columns concerning the entire career start with “C”
```{r Hitters data}
library(ISLR)
data(Hitters)
summary(Hitters)
summary(Hitters[,8:14])
str(Hitters)
```

## scatter plot

A scatter plot with two panels created in ggplot2 with the players' salaries in relation
to the number of runs, where dots should be coloured by league and one panel should show
the E division, the other the W division. The black-white theme should be used and the
Dark2 colour palette.

```{r player salaries, echo=FALSE, message=FALSE}
library(ggplot2)

ggplot(Hitters, aes(x=Runs, y=Salary, colour=League)) +
  geom_point()+
  facet_wrap(~Division)+
  scale_colour_brewer(palette="Dark2")+
  theme_bw()
```
## violin plot
A violin plot with two panels created in ggplot2 with the players' number of runs
in different divisions. One panel should show the A league, the other the N league.
The plots should be coloured according to the division, with a transparency level equal
to 0.8. The light theme (theme_light) should be used and the Set1 colour palette
```{r violin}
ggplot(Hitters, aes( Division,Runs,fill=Division)) +
  geom_violin( trim=FALSE ,alpha=0.8) +
  scale_fill_brewer(palette="Set1") +
  facet_wrap(~League)+
  theme_light()
```
# table summary
2x2 table summarising the number of players in the leagues and divisions
```{r table summary}
a= table(Hitters$League, Hitters$Division)
kable(a, caption = "League Vs Division")
```
# Table 2
A 2x2 table summarising the number of players in the leagues at the end of 1986 (League)
and the beginning of 1987 (NewLeague).
```{r table summary 2}
kable(table(Hitters$League, Hitters$NewLeague), caption = "League Vs Division")
```
# Statistical test
Statistical test results verifying the association between leagues at the end of 1986
(League) and the beginning of 1987 (NewLeague).
```{r Statistical test, message= FALSE, eval=FALSE}
Result<- t.test(Hitters$League~ Hitters$NewLeague, data=Hitters)
Result$statistic
Result$p.value

```
```{r}
tb = table(Hitters$League, Hitters$NewLeague)
tb
results <- fisher.test(tb) 
results$p.value 
results$estimate
```

